D3064R0: OOTA Execution is Provably Vacuous

### 2023-11-29 ootavacuous.tex
Apply paper number and self-review
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\begin{document}
\title{DNNNNR0: OOTA Execution is Provably Vacuous}

@@

@@

Some executable C++ memory models correctly flagged executions involving
OOTA~\cite{JadeAlglave2014HerdingCats}.\footnote{
	Others cleverly avoid this issue by forbidding atomic
	stores of non-constant values~\cite{MarkBatty2011cppmem}.}
% @@@ Better herd7 C11 citation?
However, because these models are atemporal, they cannot reject
OOTA executions other than by flagging the OOTA value as arbitrary
(which they in fact do).

@@

\section{Correct Implementations Cannot Form OOTA Cycles}
\label{sec:Correct Implementations Cannot Form OOTA Cycles}

>>>>

\begin{document}
\title{D3064R0: OOTA Execution is Provably Vacuous}

@@

This section provides a brief overview of the OOTA problem followed
by an equally brief summary of prior work in this area.

@@

All OOTA workers owe a debt to the foundational work in the infamous
``Causality Test Cases''.\footnote{
	\url{http://www.cs.umd.edu/~pugh/java/memoryModel/unifiedProposal/testcases.html}.}

Some executable C++ memory models correctly flagged executions involving
OOTA~\cite{JadeAlglave2014HerdingCats}.\footnote{
	Others cleverly avoid this issue by forbidding atomic
	stores of non-constant values~\cite{MarkBatty2011cppmem}.}
% @@@ Better herd7 C11 citation?
However, because these models are atemporal, they cannot reject
OOTA executions other than by flagging the OOTA value as arbitrary
(which some in fact do).

@@

\subsection{Correct Implementations Cannot Form OOTA Cycles}
\label{sec:Correct Implementations Cannot Form OOTA Cycles}
